### 2017-04-08 doc/manual/version3/inputParameters.tex
Minor improvements to magnetic drifts

{\ttfamily magneticDriftScheme} = 5: Magnetic drift as defined in
Eqs.~(46--48) in \cite{Sugama2016}. The function $\alpha$
 is chosen as $\alpha=(1-\xi^2)/(1+\xi^2)$ for the terms
in Eq.~(48) proportional to the normal curvature, which are the terms
that need
to be regularized at $\xi=\pm 1$.\\
(This {\ttfamily magneticDriftScheme} only works for .bc magnetic
geometry input files so far)\\

>>>>

{\ttfamily magneticDriftScheme} = 5: Magnetic drift as defined in
Eqs.~(46--48) in \cite{Sugama2016}. The function $\alpha$
 is chosen as $\alpha=(1-\xi^2)/(1+\xi^2)$ for the terms
in Eq.~(48) proportional to the normal curvature, which are the terms
that need
to be regularized at $\xi=\pm 1$.\\

{\ttfamily magneticDriftScheme} = 6: Same as {\ttfamily magneticDriftScheme} 5,
except that no regularization is applied to the magnetic drift terms multiplying $\partial f/\partial \theta$
and $\partial f/\partial\zeta$. Regularization is still applied to the magnetic drift term multiplying $\partial f/\partial \xi$.\\

{\ttfamily magneticDriftScheme} = 7: Same as {\ttfamily magneticDriftScheme} 1,
except the contribution to $\dot{\xi}$ from the magnetic drifts is dropped.\\

{\ttfamily magneticDriftScheme} = 8: Same as {\ttfamily magneticDriftScheme} 1,
except the magnetic shear term for axisymmetry is added to the coefficient of $\partial f/\partial \zeta$.
There is no change to the coefficient of $\partial f/\partial\theta.$ This option only makes sense for straight field line coordinates
and nearly axisymmetric geometry.\\

{\ttfamily magneticDriftScheme} = 9: Same as {\ttfamily magneticDriftScheme} 1,
except the magnetic shear term for axisymmetry is added to the coefficient of $\partial f/\partial \theta$.
There is no change to the coefficient of $\partial f/\partial\zeta.$ This option only makes sense for straight field line coordinates
and nearly axisymmetric geometry.\\
